Crunching Large Graphs with Commodity Processors

### 2011-04-21 doc/hotpar2011/softxmt-hotpar2011.tex
memory concurrency small edit

To enable concurrency in memory references, we break each read or
write into two operations: the {\em issue} operation and the {\em
  complete} operation. The read issue operation starts data moving
towards the processor and returns immediately, like a prefetch; the
read complete operation blocks until data is available. The write
issue operation takes data along with an address, and starts an
asynchronous write; the write complete operation blocks until the
write is committed.

@@

% cache pressure figure
\begin{figure}[t]
  \begin{center}
%    \includegraphics[width=0.48\textwidth]{figures/cachepressurenewview-edited.pdf}
    \includegraphics[width=0.48\textwidth]{figures/cachepressure-64to4M-edited2.pdf}
  \end{center}
%  \vspace{-10pt} %space with fig
  \caption{Cache pressure with coroutines, on six cores. The vertical
    axis is remote reference rate, with (a) 8 coroutines per core, and
    (b) 48 coroutines per core, about the number required for the
    network rate in the simulated delay experiments. }
  \vspace{-1.5pt} % space with text
  \label{fig:cache-pressure}
\end{figure}

>>>>

To enable concurrency in memory references, we break each read or
write into two operations: the {\em issue} operation and the {\em
  complete} operation. The read issue operation starts data moving
towards the processor and returns immediately, like a prefetch. The
read complete operation blocks until data is available. The write
issue operation takes data along with an address, and starts an
asynchronous write. The write complete operation blocks until the
write is committed.

@@

% cache pressure figure
\begin{figure}[t]
  \begin{center}
  \vspace{-10pt}
%    \includegraphics[width=0.48\textwidth]{figures/cachepressurenewview-edited.pdf}
    \includegraphics[width=0.50\textwidth]{figures/cachepressurenewview-edited.pdf}
  \end{center}
  \vspace{2pt}
%  \vspace{-10pt} %space with fig
  \caption{Cache pressure with coroutines, on six cores. The vertical
    axis is remote reference rate, with (a) 8 coroutines per core, and
    (b) 48 coroutines per core, about the number required for the
    network rate in the simulated delay experiments. }
  \vspace{-1.5pt} % space with text
  \label{fig:cache-pressure}
\end{figure}
